### 2015-07-21 rscripts/data_review.Rmd
draft 9x9 plot

```{r, echo=F}
duration_breaks <- censor.dt[,quantile(logout-login, probs=(1:2)/3)]
daily_login_breaks <- censor.dt[,.N,by=list(location_id, login_day)][,quantile(N,probs=(1:2)/3)] ## TODO zeros?
# for 90 day window
#  for extant locations
#   - what percent of active days fall in each login category?
#   - what percent of logins fall in each login category?
```

>>>>

```{r, echo=F}
duration_breaks <- censor.dt[,quantile(logout-login, probs=(1:2)/3)]
daily_login_breaks <- censor.dt[,.N,by=list(location_id, login_day)][,quantile(N,probs=(1:2)/3)] ## TODO zeros?
duration_group.dt <- censor.dt[90 <= login_day & login_day < 180, 
  list( # initial pass to get temp variables
    low = sum(logout - login < duration_breaks[1]),
    mid = sum(logout - login < duration_breaks[2]),
    high = .N
  ), 
  keyby=location_id
][,
  list( # use temp vars to calc actuals
    low = low/high,
    mid = (mid-low)/high,
    high = (high-mid)/high
  ),
  keyby=location_id
]

login_group.dt <- censor.dt[90 <= login_day & login_day < 180, 
  list(count = .N), 
  by=list(login_day, location_id)
][,
  list( # initial pass to get temp variables
    low = sum(count < daily_login_breaks[1]),
    mid = sum(count < daily_login_breaks[2]),
    high = .N
  ), 
  keyby=location_id
][,
  list( # use temp vars to calc actuals
    low = low/high,
    mid = (mid-low)/high,
    high = (high-mid)/high
  ),
  keyby=location_id
]

cross_data.dt <- merge(
  melt(
    duration_group.dt, id.vars = "location_id",
    value.name="membership", variable.name="group"
  ),
  melt(
    login_group.dt, id.vars = "location_id",
    value.name="membership", variable.name="group"
  ),
  by = "location_id",
  allow.cartesian = T,
  suffixes = c(".duration",".login")
)

ggplot(cross_data.dt) + theme_bw() +
  facet_grid(group.duration ~ group.login, labeller = function(var, val) {
    paste0(val,ifelse(var == "group.duration"," duration"," logins"))
  }) +
  aes(x=location_id, y = membership.duration*membership.login) +
  geom_point()
# for 90 day window
#  for extant locations
#   - what percent of active days fall in each login category?
#   - what percent of logins fall in each login category?
```
